### 2023-10-25 chapters/background.tex
Change references and add todos

@@

\todo[inline]{Briefly hold the readers hand and tell them why VAEs are relevant to the overarching project.}

@@

We can subdivide the inference gap \cite{cremer_inference_2018}: 
By amortizing the variational inference we introduce a gap compared to the alternative of fitting a posterior per data point, $q^{*}_{\xb}(\zb)$. This amortization gap can be reduced by using large capacity amortized posteriors. 
In cases where the true posterior does not belong to the model class of the variational family of posteriors that we fit, the inference gap cannot be reduced to zero and the remaining gap is referred to as the approximation gap.

\todo[inline]{Finish this with the parsimony gap}

@@

\todo[inline]{Derive and introduce the IWAE bound.}

@@

\paragraph{Self"=supervised learning}
An alternative approach to representation learning is provided by self"=supervised learning \parencite{mikolov_efficient_2013,devlin_bert_2018,chen_simple_2020,schneider_wav2vec_2019} which is a form of unsupervised learning where the training objective is derived from the data itself. 
While it is fair to say that not all self"=supervised training objectives are as well-motivated as the ELBO is for VAEs, they have shown impressive results within the fields of natural language processing \parencite{devlin_bert_2018,chen_simple_2020}, speech processing \parencite{schneider_wav2vec_2019}, and computer vision \parencite{chen_simple_2020}. 
For a deeper comparison of VAEs and self"=supervised methods for speech processing, we refer the reader to our paper \textcite{borgholt_brief_2022} included in \cref{app:paper-brief}. 
\Cref{chp:paper-review} provides a comprehensive introduction to and review of self"=supervised learning in speech recognition.

>>>>

\todo[inline]{Briefly hold the readers hand at actualize the importance of OODD.}

@@

\moretodo[inline]{Briefly hold the readers hand and tell them why VAEs are relevant to the overarching project.}

@@

We can subdivide the inference gap \cite{cremer_inference_2018}: 
By amortizing the variational inference we introduce a gap compared to the alternative of fitting a posterior per data point, $q^{*}_{\xb}(\zb)$. This amortization gap can be reduced by using large capacity amortized posteriors. 
In case the true posterior does not belong to the model class of the variational family of posteriors that we fit, the inference gap cannot be reduced to zero and the remaining gap is referred to as the approximation gap.

\moretodo[inline]{Finish this with the parsimony gap}

@@

\moretodo[inline]{Derive and introduce the IWAE bound.}

@@

\paragraph{Self"=supervised learning}
\moretodo[inline]{Revise according to change of review papers.}
An alternative approach to representation learning is provided by self"=supervised learning \parencite{mikolov_efficient_2013,devlin_bert_2018,chen_simple_2020,schneider_wav2vec_2019} which is a form of unsupervised learning where the training objective is derived from the data itself. 
While it is fair to say that not all self"=supervised training objectives are as well-motivated as the ELBO is for VAEs, they have shown impressive results within the fields of natural language processing \parencite{devlin_bert_2018,chen_simple_2020}, speech processing \parencite{schneider_wav2vec_2019}, and computer vision \parencite{chen_simple_2020}. 
For a deeper comparison of VAEs and self"=supervised methods for speech processing, we refer the reader to our paper \textcite{borgholt_brief_2022} included in \cref{chp:paper-brief}. 
\Cref{app:paper-review} provides a comprehensive introduction to and review of self"=supervised learning in speech recognition.

### 2023-10-25 chapters/main-contributions.tex
Change references and add todos

\todo[inline]{Revise the location of the benchmarking paper and change the SSL review to the SSL+LVM brief review. Revise the text here accordingly.}

@@

\contribitem{part:unsupervised-speech-representation-learning}
This part of the thesis is concerned with self"=supervised speech representation learning and consists of a single paper that provides a substantial review of the field \parencite{mohamed_selfsupervised_2022}. 
Self"=supervised learning is a promising approach to speech representation learning that has shown a fast, wide and successful adoption across speech modelling over the course of the last few years. 
As measured by performance on common downstream tasks such as speech recognition and spoken language understanding, self"=supervised representations generally outperform representations learned via probabilistic generative models such as those investigated in \cref{part:unsupervised-uncertainty-estimation}. 
In this review paper, we do not consider uncertainty estimation, but in future work, consideration should be given to the use of self"=supervised learning for learning representations for unsupervised uncertainty estimation. 
We shall return to this in the discussion of \cref{chp:paper-review} in \cref{sec:discussion-paper-review}.
\todo[inline]{Edit this if we did not discuss this.}
An early version of this review paper included a review of variational autoencoders for speech representation learning and a comparison between the two modelling paradigms \parencite{borgholt_brief_2022}. 
Due to a desire to focus on self"=supervised methods, the paper in \cref{chp:paper-review} does not put particular focus on variational methods. 
The early version is included in \cref{app:paper-brief} for reference.

\contribitem{chp:paper-review}
This paper provides a comprehensive review of self"=supervised speech representation learning. Previous work is grouped into three main categories of methods: contrastive, autoregressive, and generative, and the methods are compared in terms of their training objectives, model architectures, and performance on downstream tasks. The review also provides a discussion of the current state of the field and promising future directions of research.

>>>>

\moretodo[inline]{Revise the location of the benchmarking paper and change the SSL review to the SSL+LVM brief review. Revise the text here accordingly. $\downarrow$}

@@

\contribitem{part:unsupervised-speech-representation-learning}
This part of the thesis is concerned with self"=supervised speech representation learning and consists of a single paper that provides a substantial review of the field \parencite{mohamed_selfsupervised_2022}. 
Self"=supervised learning is a promising approach to speech representation learning that has shown a fast, wide and successful adoption across speech modelling over the course of the last few years. 
As measured by performance on common downstream tasks such as speech recognition and spoken language understanding, self"=supervised representations generally outperform representations learned via probabilistic generative models such as those investigated in \cref{part:unsupervised-uncertainty-estimation}. 
In this review paper, we do not consider uncertainty estimation, but in future work, consideration should be given to the use of self"=supervised learning for learning representations for unsupervised uncertainty estimation. 
We shall return to this in the discussion of \cref{app:paper-review} in \cref{sec:discussion-paper-review}.
\moretodo[inline]{Edit this if we did not discuss this.}
An early version of this review paper included a review of variational autoencoders for speech representation learning and a comparison between the two modelling paradigms \parencite{borgholt_brief_2022}. 
Due to a desire to focus on self"=supervised methods, the paper in \cref{app:paper-review} does not put particular focus on variational methods. 
The early version is included in \cref{chp:paper-brief} for reference.

\contribitem{app:paper-review}
This paper provides a comprehensive review of self"=supervised speech representation learning. Previous work is grouped into three main categories of methods: contrastive, autoregressive, and generative, and the methods are compared in terms of their training objectives, model architectures, and performance on downstream tasks. The review also provides a discussion of the current state of the field and promising future directions of research.

\moretodo[inline]{Revise the location of the benchmarking paper and change the SSL review to the SSL+LVM brief review. Revise the text here accordingly. $\uparrow$}
